`make.modifiers`

### 2020-11-13 inst/gitbook/03_make.modifiers.Rmd
First manual version

>>>>

## Demo runnable

```{r, fig.height = 16, fig.width = 8}
bd.params <- list(speciation = 1, extinction = 1/3)
traits <- make.traits()
stop.rule <- list(max.taxa = 20, max.living = Inf, max.time = Inf)
modifiers <- NULL
events <- NULL
null.error <- NULL

## modifiers
condition <- function(trait.values, parent.lineage) return(parent.traits(trait.values, parent.lineage) < 0)
modify <- function(x) return(x * 20)

## Setting up the different modifiers
modify_speciation <- make.modifiers(speciation    = speciation.trait,
                                    condition     = condition,
                                    modify        = modify)
modify_brlen <- make.modifiers(branch.length = branch.length.trait,
                               condition     = condition,
                               modify        = modify)
modify_speciation_brlen <- make.modifiers(branch.length = branch.length.trait,
                                          speciation    = speciation.trait,
                                          condition     = condition,
                                          modify        = modify)

## Test normal (no modifiers)
set.seed(1)
test <- dads(bd.params, stop.rule, traits, null.error = 20)
par(mfrow = c(4,2))
plot(test$tree)
plot.dads(test, main = "random tree + trait")

## Test with modifiers
set.seed(1)
trait_table <- NULL
test <- dads(bd.params, stop.rule, traits,
                                modifiers = modify_speciation,
                                null.error = 20)
plot(test$tree)
plot.dads(test, main = "Skewed speciation")

set.seed(1)
trait_table <- NULL
test <- dads(bd.params, stop.rule, traits,
                                modifiers = modify_brlen,
                                null.error = 20)
plot(test$tree)
plot.dads(test, main = "Skewed branch length")

set.seed(1)
trait_table <- NULL
test <- dads(bd.params, stop.rule, traits,
                                modifiers = modify_speciation_brlen,
                                null.error = 20)
plot(test$tree)
plot.dads(test, main = "Skewed branch length and speciation")

```
